---
title: "Checks"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(openxlsx)
data.path <- "C:/Rprojects/neonet/inst/extdata/"
data.name <- "140_140_id00140_doc_elencoc14.tsv"
data.idf <- paste0(data.path, data.name)
data.df <- read.csv(data.idf, sep = "\t", header = TRUE)

legend.n.tot <- function(x){
  text <- paste0("<span style='color:green'><b>", x,"</b></span>")
  return(text)
}

legend.n.disp <- function(x){
  text <- paste0("<span style='color:red'><b>", x,"</b></span>")
  return(text)
}

legend.var <- function(n.disp.records, n.tot.rec){
  text <- paste0("<span style='color:red'><b>", n.disp.records,"</b></span>", 
                 "/",
                 "<span style='color:green'><b>", n.tot.rec,"</b></span>")
  return(text)
}
```

This Rmd document identify correct records (`OK`) and ones with issues (`KO`).  

**Correctness of records is checked by studied variable**. In <span style='color:red'><b>red</b></span>, the number of available records for this variable. In <span style='color:green'><b>green</b></span>, the total number of records in the original dataset, e.g. `r legend.var(2455, 2500)`. The difference between these two numbers is number of missing data for this studied variable.  


## Summary

```{r Summary, echo=FALSE, warning = FALSE, message = FALSE}
#The identifier (`idf`) of the individuals is the LabCode columns by default
n.tot.rec <- nrow(data.df)
n.tot.var <- ncol(data.df)
```

The total number of records in the original dataset is `r legend.n.tot(n.tot.rec)`. These records are described by `r n.tot.var` variables:

```{r SummaryVar, echo=FALSE, warning = FALSE, message = FALSE}
library(knitr)
library(kableExtra)
data.df <- as.data.frame(sapply(data.df, function(x) trimws(x)))   # rm leading/trailing spaces
data.df.classes <- sapply(data.df, class)
kable(data.df.classes)
```


## Coordinates


```{r coordinates, echo=FALSE, warning = FALSE, message = FALSE}
library(dplyr)
library(leaflet)
# working copy
df.coord <- data.df
# convert to appropriate type
df.coord$Longitude <- as.numeric(df.coord$Longitude)
df.coord$Latitude <- as.numeric(df.coord$Latitude)
### collect KO dates
## NA data
# Long
df.coord.long.ko <- df.coord[is.na(data.df$Longitude), ]
df.coord.long.ko.idf <- df.coord.long.ko$LabCode
# Lat
df.coord.lat.ko <- df.coord[is.na(data.df$Latitude), ]
df.coord.lat.ko.idf <- df.coord.lat.ko$LabCode
# Long or Lat
df.coord.ko <- df.coord[(is.na(df.coord$Longitude) | is.na(df.coord$Latitude)), ]
### collect OK dates
df.coord.ok <- df.coord[(!is.na(df.coord$Longitude) & !is.na(df.coord$Latitude)), ]
n.disp.records <- n.tot.rec - nrow(df.coord.ko)
legend.var.txt <- legend.var(n.disp.records, n.tot.rec)
leaflet(width = "80%", height = "600px") %>%
  addTiles(group = 'OSM') %>%
  addControl(legend.var.txt, 
             position = "bottomright") %>%
  addProviderTiles(providers$Esri.WorldImagery, group='Esri.WorldImagery') %>%
  addMarkers(df.coord.ok$Longitude,
             df.coord.ok$Latitude,
             label = df.coord.ok$SiteName) %>%
  addLayersControl(
    baseGroups = c('OSM', 'Esri.WorldImagery')) %>%
  addScaleBar(position = "bottomleft")
```
